Notes on scheduling the SAA2019 meeting

### 2017-11-03 analysis/paper/saa2018_posters.Rmd
posters need to avoid clash with papers

```{r}
# poster session durations
poster_session_durations <- 
  read_excel("../data/raw_data/saa all organizedsession_timeslotABv3.xls", 
             sheet = "Posters1")
```

>>>>

```{r}
# poster session durations
poster_session_durations <- 
  read_excel("../data/raw_data/saa all organizedsession_timeslotABv3.xls", 
             sheet = "Posters1")
# add day-part to compare with papers
poster_session_durations <- 
  poster_session_durations %>% 
  mutate(start = as.character(start)) %>% 
  mutate(end = as.character(end)) %>% 
  mutate(day_part = case_when(
    start == "1899-12-31 08:00:00" ~ "morning",
    start == "1899-12-31 10:30:00" ~ "morning",
    start == "1899-12-31 14:00:00" ~ "afternoon",
    start == "1899-12-31 17:00:00" ~ "evening"
  ))
```

We want to avoid people giving a poster and a talk at the same time, so we need to check with the paper schedule:

```{r}
sessions_in_day_parts_data_with_all_names_df <- 
  read_csv("../data/derived_data/sessions_in_day_parts_data_with_all_names_df.csv")
```
